What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Fixing typo

\medskip\noindent\EE{$min(e)=\c{model.frame}$} The \c{model.frame} function
returns a dataframe resulting from f fitting the model described in a given
formula. This form subsumes \c{F(F(X))}, \c{FUN}, and assignments. It is the
single most popular function invoked from \eval; it occurs in 7\% of the sites.
Each call does quite a lot of work with a 2K instructions median.

>>>>

\medskip\noindent\EE{$min(e)=\c{model.frame}$} The \c{model.frame} function
returns a dataframe resulting from fitting the model described in a given
formula. This form subsumes \c{F(F(X))}, \c{FUN}, and assignments. It is the
single most popular function invoked from \eval; it occurs in 7\% of the sites.
Each call does quite a lot of work with a 2K instructions median.
